Generalized Plackett-Luce Likelihoods

### 2022-08-13 inst/jss_hyper3.Rnw
more rewording

If we allow non-finishers [that is, a subset of competitors who are
beaten by all the ranked competitors], there is another nontrivial
order statistic, viz $a\succ b\succ\left\lbrace a,b\right\rbrace$
[thus one of the two $a$'s won, one of the $b$'s came second, and one
of each of $a$ and $b$ failed to finish].

@@

Further work might include a systematic comparison between
\code{hyper3} approach and the Mann-Whitney-Wilcoxon test, including
the characterisation of the power function of both tests.  Further,
the package could easily be extended to allow non-integer
multiplicities, which might prove useful in the context of reified
Bradley Terry techniques~\citep{hankin2020}.

>>>>

If we allow non-finishers---that is, a subset of competitors who are
beaten by all the ranked competitors: \cite{turner2020} call this a
{\em top $n$ ranking}), there is another nontrivial order statistic,
viz $a\succ b\succ\left\lbrace a,b\right\rbrace$ [thus one of the two
  $a$'s won, one of the $b$'s came second, and one of each of $a$ and
  $b$ failed to finish].

@@

Draws are not considered in the present work but in principle may be
accommodated, either using likelihoods comprising sums of
Plackett-Luce probabilities~\citep{hankin2017}; or the introduction of
a reified draw entity~\citep{hankin2020}.

Further work might include a systematic comparison between
\code{hyper3} approach and the Mann-Whitney-Wilcoxon test, including
the characterization of the power function of both tests.  The package
could easily be extended to allow non-integer multiplicities, which
might prove useful in the context of reified Bradley Terry
techniques~\citep{hankin2020}.
